---
title: "Young Statisticians Conference 2017"
author: "Statistical Society of Australia"
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(googlesheets)
library(ggmap)
```


```{r Get map info, include = F}
# Get registration info from gs.
map.data <- gs_title("ysc2017") %>% 
  gs_read("registrations") %>% 
  group_by(city.town) %>% 
  summarise(count = n()) 

# Get lon and lat for each city/town.
map.data <- map.data %>% 
  cbind(geocode(map.data$city.town))

# Create map plot.
map.plot <- qmap("Australia", zoom = 4, maptype = "watercolor") +
    geom_point(aes(x = lon,
                   y = lat,
                   size = count),
               data = map.data,
               alpha = 0.5,
               colour = "darkgreen") +
  labs(title = "Where people are coming from")
```

TESTING

***

On behalf of the [Statistical Society of Australia](http://www.statsoc.org.au/), the YSC organising committee warmly invites you to join us in the Gold Coast at our biennial conference for early career researchers in statistics.

***

The conference will be held over two days, **Tuesday 26 and Wednesday 27 of September** from **9am to 5pm** each day. In addition to the formal schedule, there will also be social events and possibly workshops. 

As the organising committee finalises details, announcements will be made via the SSA members' list.   

***

```{r, echo = F, fig.align='center'}
map.plot
```


```{r, echo = F, include = F}
main.dates <- data.frame(Date = dmy("26/09/2017", "27/09/2017"),
                         Time = rep(c("9:00am - 5:00pm"), 2)) %>% 
  mutate(Day = wday(Date, label = T, abbr = F)) %>% 
  select(Day, Date, Time)
knitr::kable(main.dates)
```