---
title: "Venue, accommodation, and travel"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(googlesheets)
library(ggmap)

# Get venue data
venue.data <- gs_title("ysc2017") %>% 
  gs_read("venue")



```

# Venue

```{r Get map info, include = F}
# First venue for the conference, second for accommodation?

# Get lon and lat for each city/town.
map.data <- venue.data %>% 
  cbind(geocode(venue.data$venue.address))

# Create map plot.
map.plot <- 
  qmap(map.data$venue.address[1], zoom = 12, maptype = "roadmap") +
    geom_point(aes(x = lon,
                   y = lat),
               data = map.data[1,],
               alpha = 0.5,
               size = 5,
               colour = "darkgreen") 
```

```{r, echo = F, fig.align="center"}
map.plot
```


```{r, echo = FALSE}
knitr::kable(venue.data,
             col.names  = c("Venue name", "Address", "Phone"))
```

# Where to stay 

Delegates of YSC2017 receive a **special discount** when booking their accommodation at the [Mantra Twin Towns](http://www.mantra.com.au/queensland/gold-coast/coolangatta/accommodation/resorts/mantra-twin-towns/).  

The hotel offers a choice of hotel rooms or one, two and three bedroom apartments. Gather some friends around and save even more by sharing an apartment! 

**Hotel Rooms – including breakfast**

- Hotel Room (Queen Bed) $165.00 per night
- Hotel Deluxe Twin Room (Two Queen Beds) $185.00 per night

**Fully Self Contained Apartments – breakfast not included**

- 1 Bedroom (up to 2 persons) $165.00 per night
- 2 Bedroom (up to 4 persons) $245.00 per night

**These special rates cannot be booked online. Please use the booking [form](https://drive.google.com/file/d/0Bwx_ciAkl_MZeG1lbEZ5QUdHaFU/view?usp=sharing).**

Located at the Southern tip of the Gold Coast, Mantra Twin Towns is the ideal place to stay if you’d not only like to stay close to the conference venue, but also be close to all the main attractions in Coolangatta and the Tweed Coast. From this Coolangatta accommodation it’s just a short stroll to the famous Greenmount beach or beautiful Rainbow Bay where the Quicksilver Roxy Pro is held annually - enjoy a swim or stroll along Marine Parade to soak in the sea views. When it comes to entertainment - you only need to walk through the covered walkway and you’re surrounded by restaurants, bars and everything on offer at the Twin Towns Services Club. 

# Getting there

Getting to Tweed Heads is easy thanks to its accessibility from most popular capital cities and region centres.

## By Air

Those flying into Tweed Heads can choose to arrive at the Brisbane Airport, Gold Coast Airport or the Ballina/Byron Gateway Airport. The Gold Coast Airport is the closest to Tweed Heads at just 4km away however the Brisbane Airport also offers easy access to Tweed Heads via the Airtrain or the Pacific Motorway. If you're travelling from the south, the Ballina/Byron Gateway Airport provides easy access from regional and domestic centres and all airports offer the convenience of transfer services and car hire.

## By Car

The most convenient way to drive to Tweed Heads is via the country's main highway on the east coast, the Pacific Motorway. Passing directly through Brisbane, the Gold Coast, Tweed Heads and further south to Byron Bay and Ballina, the Pacific Coast offers a legendary touring route of which Tweed Heads is most definitely a highlight. If you have a little extra time on your trip, there are also a number of other routes that offer a more scenic drive to Tweed Heads from Brisbane, the Gold Coast, Byron Bay and Lismore.

## By Bus/Coach

The Tweed region and surrounds enjoy an extensive network of public transport which offers over 480 services daily. Services operate within the Tweed region to shopping centres, local destinations and attractions. There are also regular bus services operated by Premier and Greyhound Australia which provide transport to and from Brisbane, the Gold Coast, Byron Bay and as far south as Sydney.

## By Train

There are a number of rail networks that link Tweed Heads to surrounding regions however there is also an express airport rail link known as the 'Airtrain' that travels between the Brisbane Airport, Brisbane City and the Gold Coast. Regular services are operated daily until 10pm with connections available from the Gold Coast to Tweed Heads. 